---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# classifyNMIBC

This package implements a Pearson nearest-centroid classifier that assigns class labels to single samples according to the four transcriptomic UROMOL2021 classes of non-muscle-invasive bladder cancer (NMIBC): class 1, class 2a, class 2b and class 3.

The classifier code was adapted from the consensusMIBC classifier: Kamoun, A et. al. A Consensus Molecular Classification of Muscle-invasive Bladder Cancer, Eur Urol (2019), doi: https://doi.org/10.1016/j.eururo.2019.09.006
Both classifiers can be found on our online web application: http://nmibc-class.dk

A smaller, example data set is provided to run the classifier.

## Installation

You can install the development version of classifyNMIBC from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("KaiAragaki/classifyNMIBC")
```

## Citation 

Please cite _Lindskrog and Prip et al. An integrated multi-omics analysis identifies prognostic molecular subtypes of non-muscle-invasive bladder cancer. Nat Commun. 2021. PMID: 33863885. DOI: 10.1038/s41467-021-22465-w_

## Example

```{r}
library(classifyNMIBC)
head(test_data)
```
 

``` {r}
test_data |> 
  classifyNMIBC(min_cor = 0.2, gene_id = "ensembl_gene_ID", tidy = FALSE) |> 
  head()
```

